---
title: "Social Survey 2010"
author: "Natalie Gavia"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```

From the graph, it seems to show that...

```{r}
barchartGC(~race+cappun, data=alldata, type = "percent") 
```

```{r}
barchartGC(~condrift+cappun, data=alldata, type = "percent") 
```


From the graph, it seems the results are independent from each other since each category has a difference in their favor and opposing views. For example, the big gap in favor among Black and White.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
tab = xtabs(~race+condrift, data=alldata)
rowPerc(tab)
colPerc(tab)
```


```{r}
tab = xtabs(~race+cappun, data=alldata)
rowPerc(tab)
colPerc(tab)
```

```{r}
tab = xtabs(~condrift+cappun, data=alldata)
rowPerc(tab)
colPerc(tab)
```
From the numerical results, it displays that Black people are less in favor of capital punishment compared to white people.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(~race+condrift, data=alldata, graph=TRUE)
```


```{r}
chisqtestGC(~race+cappun, data=alldata, graph=TRUE)
```

```{r}
chisqtestGC(~condrift+cappun, data=alldata, graph=TRUE)
```

From our results we are going to reject the null hypothesis because the P-Value is really low.  


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Overall, the data is not independent of each other since the total result of each race, capital punishment and continental drift were dependent of each other based of race. 
